Supermartingales and Termination Analysis of Statistical PCF

### 2021-01-12 LICS21/related.tex
Added some references

% !TEX root = main.tex
\section{Related work and further directions}

@@

\lo{Our results specialise to proving termination of non-random lambda calculus, which is much studied. Our approach is closest in spirit to Jones' work on size-change argument. Dal Lago's work builds on this. We think that martingales are a good framework for generalising / unifying with size-change work.}

@@

\lo{Kobayashi et al.: PHORS are strictly weaker in expressivity.}

\label{sec:related}
We have not yet been able to prove \Cref{conj:antitone} which would imply that \Cref{thm:antitone rankable implies termination} is almost complete.
\begin{conjecture}
\label{conj:antitone}
Every term is antitone rankable if all of the terms reachable from it are AST.
\end{conjecture}

>>>>

% !TEX root = main.tex
\section{Related work and further directions}
\label{sec:related}

@@

\lo{Our results specialise to proving termination of non-random lambda calculus, which is much studied. Our approach is closest in spirit to Jones' work on size-change principle \cite{DBLP:journals/lmcs/JonesB08,DBLP:conf/aplas/SereniJ05}. Dal Lago's \cite{DBLP:journals/toplas/LagoG19} work builds on this. We think that martingales are a good framework for generalising / unifying with size-change work.}

@@

\lo{Kobayashi et al.: PHORS are strictly weaker in expressivity \cite{DBLP:conf/lics/KobayashiLG1}.}

We have not yet been able to prove \Cref{conj:antitone} which would imply that \Cref{thm:antitone rankable implies termination} is almost complete.
\begin{conjecture}
\label{conj:antitone}
Every term is antitone rankable if all of the terms reachable from it are AST.
\end{conjecture}
